---
title: "Developing Data Products Reproducible Pitch"
author: "Simran"
date: "21/02/2021"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

***
#Developing Data Products Assignment


##This is a task for the data science coursera course about developing data products for week 4. As part of this, I have created a shiny app and it is deployed on shiny server with the following link
https://simra.shinyapps.io/myapp1/ and the code at https://github.com/Simran-2020/datasciencecoursera



##Overview

The shiny app plots graph against miles per gallon (mpg) for different variables from the mtcars dataset.We observe that there is a strong correlation between wt and mpg.This project suggests that if you want to have high miles per gallon (mpg), buy a car with low weight (wt)!

***
### Let us see the mtcars dataset

```{r}
library(dplyr)
library(explore)
mtcars %>% describe()
```
***

UI Code
```{r}
library(shiny)


# Define UI for miles per gallon app ----
ui <- fluidPage(
    
    # App title ----
    titlePanel("Miles Per Gallon"),
    
    # Sidebar layout with input and output definitions ----
    sidebarLayout(
        
        # Sidebar panel for inputs ----
        sidebarPanel(
            
            # Input: Selector for variable to plot against mpg ----
            selectInput("variable", "Variable:",
                        c("Cylinders" = "cyl",
                          "Weight (lb/1000)" = "wt",
                          "Transmission" = "am",
                          "Gears" = "gear",
                          "Displacement (cu.in.)" = "disp",
                          "Gross horsepower" = "hp",
                          "Rear axle ratio" = "drat",
                          "1/4 mile time" = "qsec",
                          "V/S" = "vs",
                          "Number of carburetors" = "carb"
                        )),
            
            # Input: Checkbox for whether outliers should be included ----
            checkboxInput("outliers", "Show outliers", TRUE)
            
        ),
        
        # Main panel for displaying outputs ----
        mainPanel(
            
            # Output: Formatted text for caption ----
            h3(textOutput("caption")),
            
            # Output: Plot of the requested variable against mpg ----
            plotOutput("mpgPlot")
            
        )
    )
)
```
***

Server Code

```{r}
library(shiny)

mpgData <- mtcars
mpgData$am <- factor(mpgData$am, labels = c("Automatic", "Manual"))

# Define server logic to plot various variables against mpg ----
server <- function(input, output) {
    
    # Compute the formula text ----
    # This is in a reactive expression since it is shared by the
    # output$caption and output$mpgPlot functions
    formulaText <- reactive({
        paste("mpg ~", input$variable)
    })
    
    # Return the formula text for printing as a caption ----
    output$caption <- renderText({
        formulaText()
    })
    
    # Generate a plot of the requested variable against mpg ----
    # and only exclude outliers if requested
    output$mpgPlot <- renderPlot({
        boxplot(as.formula(formulaText()),
                data = mpgData,
                outline = input$outliers,
                col = "#75AADB", pch = 19)
    })
    
}

```




  